\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
pass

\section{Methodology}

\begin{table}
  \centering
  \label{table:bug-characterization}
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{l|rrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{r}{build}          &   \multicolumn{1}{r}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}

Our dataset currently consists of \numbugs{} instances of reproducible
bugs representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of bug
instances based on releases of the library against those based on
nightly builds, and column ``environment'' shows the breakdown of bug
instances that use Python's virtual environment against those that run
on a Docker container.

\subsection{Selection of Libraries}

@@

\subsection{Selection of Bugs}

\Fix{Abid, explain the selection criterion for the bugs.}

\subsection{Challenges in Bug Reproduction}

\textbf{Handling bugs from nighly builds require saving wheels.}  Many
of the reproducible bugs rely on nightly builds since they can not be
reproduced with any release builds. These nightly builds have a
limited amount of time when they are publicly available, and they are
de-indexed and removed after that time. In order to ensure bugs that
depend on these nightly builds can be reproduced after these builds
disappear, we save the whl files of these builds.

\textbf{Handling bugs in specific GPU-CUDA versions require OS
  changes:} Many of the GPU-related bugs can only be repro duced with
specific GPU builds and specific CUDA builds. Changing different
virtual environments does not change the CUDA versions of the
system. That is why we use Docker when a bug relies on a specific
version of CUDA to be installed in the system.

\subsection{Method}

\Fix{Abid, explain the method we used to create a bug instance}

\section{\tname: Database of Bugs in DL libraries}
\subsection{Bug Interface}
\subsection{Test Oracle}
\subsection{Usage and Setup}

>>>>

\section{Objects and Methods}

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of reproducible bugs from \tname.}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
  \\ \bottomrule
\end{tabular}
\end{table}

This section describes the criteria for selecting libraries and bugs
(Section~\ref{sec:selection-criterion}), the challenges for bug
reproduction (Section~\ref{sec:challenges}), and the method we
followed to create bug instances (Section~\ref{sec:method}). The
\tname\ database consists of \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of bug
instances based on releases of the library against those based on
nightly builds, and column ``environment'' shows the breakdown of bug
instances that use Python's virtual environment against those that run
on a Docker container.

\subsection{Selection Criterion}
\label{sec:selection-criterion}

@@

\Fix{Abid, explain the criterion for selecting the bugs (e.g., it
  contains test code showing the problem).}

\subsection{Challenges}
\label{sec:challenges}

\textbf{Handling bugs from nighly builds requires saving wheels.}  Many
of the reproducible bugs rely on nightly builds of the
libraries. These builds are available for a limited amount of time. In
order to ensure bugs reported on these builds to remain reproducible,
it is imperative to save wheel files~\cite{wheels} for the
correspondind builds.

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Many of the GPU-related bugs can only be repro duced with
specific GPU builds\Fix{I don't understance GPU builds. do you mean
  GPU vendor/version? give example} and specific CUDA builds. Changing
different virtual environments does not change the CUDA
versions\Fix{Do you mean ``it is not possible to change the CUDA (or
  GPU) version with Python's virtual environments''?} of the
system. That is why we use Docker when a bug relies on a specific
version of CUDA to be installed in the system.

\subsection{Method}
\label{sec:method}

\Fix{Abid, explain the steps you followed to create a bug
  isntance. For example, (1) selected an issues (according to the
  criteria defined in 2.1), (2) ...}

\section{\tname: Database of Bugs in DL libraries}
\subsection{Bug Interface}

\begin{table}
  \centering
  \caption{\label{table:bug-interface}\tname's bug interface.}
\begin{tabular}{lp{6.5cm}}
\toprule
list-tests & List the tests available on this dataset\\
run-test & Runs one test\\
run-tests & Runs all the tests\\
show-info & Shows information about the tests available on this benchmark\\
stats & Shows statistics about this dataset (e.g., number of tests
that require GPU, number of tests that reproduce bugs in C or Python
code, etc.)\\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{table:bug-interface} shows \Fix{...}

\subsection{Test Oracle}

\Fix{explain that the test passes if the bug can be reproduced}

\subsection{Usage and Setup}

\subsubsection{Running one bug instance}

\Fix{walkthrough an example. Show input and part of output. Explain
  the output.}

\subsubsection{Running FreeFuzz~\cite{wei2022free} on \tname.}

\Fix{walkthrough an example. Show input and part of output. Explain
  the output.}
